DRAFT: Factors Influencing Abundance & Virus Isolation in Mosquitoes

### 2024-03-07 products/manuscript/Manuscript.qmd
final edit
removed page break

| Data                         | Description                                                                                                                                           | Source                                |
|------------------------------|-------------------------------------------------------------------------------------------------------------------------------------------------------|---------------------------------------|
| Mosquito Surveillance Data   | Records of mosquito species counts, locations, and dates of collection. Data on the presence of EEE in mosquito populations is particularly valuable. | XXX County Mosquito Control           |
| Weather Data                 | Temperature, humidity, rainfall, and wind speed influence mosquito activity, population dynamics, and virus transmission.                             | NOAA                                  |
| Bird Population Data         | Since birds are a natural reservoir for EEE, information on bird populations and migration patterns could be relevant.                                | eBird                                 |
| Human Case Reports           | Data on confirmed human cases of EEE, including location, date of onset, and clinical outcomes.                                                       | MA Dept of Public Health publications |
| Veterinary Surveillance Data | Since horses and other mammals can also be affected by EEE, veterinary records could provide early warning signs of virus activity in an area.        | MA Dept of Public Health              |

@@

## Fullanalysis

>>>>

| Data                         | Description                                                                                                                                           | Source                                |
|--------------|--------------------------------------------|--------------|
| Mosquito Surveillance Data   | Records of mosquito species counts, locations, and dates of collection. Data on the presence of EEE in mosquito populations is particularly valuable. | XXX County Mosquito Control           |
| Weather Data                 | Temperature, humidity, rainfall, and wind speed influence mosquito activity, population dynamics, and virus transmission.                             | NOAA                                  |
| Bird Population Data         | Since birds are a natural reservoir for EEE, information on bird populations and migration patterns could be relevant.                                | eBird                                 |
| Human Case Reports           | Data on confirmed human cases of EEE, including location, date of onset, and clinical outcomes.                                                       | MA Dept of Public Health publications |
| Veterinary Surveillance Data | Since horses and other mammals can also be affected by EEE, veterinary records could provide early warning signs of virus activity in an area.        | MA Dept of Public Health              |

@@

## Full analysis
